Untitled

### 2022-10-27 draft_report.Rmd
10/27 fixed minor issues

### 1. Introduction
two different methods of haplotype reconstruction (haploqa vs qtl2)
  haploqa was written a decade ago, not well-maintained
  qtl2 is newer method. Since haploqa is not maintained, it's ideal to discontinue. However, before the transition is made, this project is in place
  to compare the results to ensure the qtl2 outputs can be used as a substitute for the haplotype reconstruction tasks that haploqa is doing.

@@

@@

```{r}
# CC
cc_pct_df <- fread(file.path(shiny_pct_fp, 'cc_truth_comp.csv'))
cc_pct_df

@@

>>>>

### 1. Introduction

@@

(some backgrounds about when the optimal models were built/what about them makes them optimal?) Some optimal models were built for each of the crosses in qtl2, which

@@

```{r}
# CC
cc_pct_df <- fread(file.path(shiny_pct_fp, 'cc_truth_comp.csv'))
cc_pct_df
#cc_pct_df
ggplot(cc_pct_df) + aes(x = qtl2_pct_diff, y = haploqa_pct_diff) + geom_point()
```

```{r}
# BXD f3
bxd_pct_df <- fread(file.path(shiny_pct_fp, 'bxd_truth_comp.csv'))
bxd_pct_df

@@

```{r}
# BXD f3
f2_pct_df <- fread(file.path(shiny_pct_fp, 'f2_truth_comp.csv'))
f2_pct_df

```{r}
do_qtl2_truth_diff <- do_pct_df$qtl2_pct_diff
cc_qtl2_truth_diff <- cc_pct_df$qtl2_pct_diff
bxd_qtl2_truth_diff <- bxd_pct_df$qtl2_pct_diff
f2_qtl2_truth_diff <- f2_pct_df$qtl2_pct_diff

# align lengths
max_n <- max(nrow(do_pct_df), nrow(cc_pct_df), nrow(bxd_pct_df), nrow(f2_pct_df))

length(do_qtl2_truth_diff) <- max_n 
length(cc_qtl2_truth_diff) <- max_n
length(bxd_qtl2_truth_diff) <- max_n
length(f2_qtl2_truth_diff) <- max_n

df_qtl2_truth_diff <- as.data.frame(cbind('do_qtl2_truth_diff' = do_qtl2_truth_diff, 'cc_qtl2_truth_diff' = cc_qtl2_truth_diff, 'bxd_qtl2_truth_diff' = bxd_qtl2_truth_diff, 'f2_qtl2_truth_diff' = f2_qtl2_truth_diff))
df_qtl2_truth_diff
```

```{r}
do_qtl2_truth_diff
```
